Spin canonical rings of log stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
edited some of brians comments

Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$.
It is well known that the canonical sheaf $\Omega _X,$ with
associated canonical divisor $K_X$, determines the {\bf canonical
map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
ring} is defined to be
\begin{align*}
	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
\end{align*}

@@

With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
of schemes.
\end{rem}
\todo{brain: Although Def. 2.3 makes sense for any $e_i > 1$, is this the “right” notion when char(k) divides some $e_i$?  (The “corresponding” stack would not be tame, for example, so I’d be hesitant to think that various notions building on Def. 2.3 are really appropriate if char(k) divides some $e_i$; of course, the main motivation comes from char. 0….).}
\begin{defn}
\label{defn:div-ex}
Let $\sx$ be a stacky curve over $k$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
Then, we notate
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

@@

\item One direction for further research is to 
		extend the results of this paper to divisors $D \in \di \sx$ on a 
		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
		divisors translate to rings of fractional weight $\frac{2}{n}$ modular
		forms. A {\bf modular form 
		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
		line bundle $\eta$ so that there exists a line bundle $\gamma$ with
$\gamma^{\otimes a} \cong \eta$ \todo{In item 2 of section 8, I see no reason to specifically focus on X(p).  (I am also skeptical that the definition given there is appropriate; for weight k/2 with odd k it seems not the right definition.  I’ve never looked at [2] or [9].)}
 and 
 $\gamma^{\otimes n} \cong \Omega_{X(p)}^1 \otimes \sco_{X(p)}(\Delta)$.
		For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
		[$\mathsection$ 6]{milnor:fractional-weight}.

>>>>

Let $X$ be a smooth proper geometrically-integral algebraic curve of genus $g$ over a field $k$.
It is well known that the canonical sheaf $\Omega _X,$ with
associated canonical divisor $K_X$, determines the {\bf canonical
map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
ring} is defined to be
\begin{align*}
	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
\end{align*}

@@

With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
of schemes.
\end{rem}

\begin{defn}
\label{defn:div-ex}
Let $\sx$ be a stacky curve over $k$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
Then, we notate
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

@@

\item One direction for further research is to 
		extend the results of this paper to divisors $D \in \di \sx$ on a 
		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
		divisors often arise as rings of fractional weight $\frac{2}{n}$ modular
		forms. For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
		[$\mathsection$ 6]{milnor:fractional-weight}.
